A pipeline to analyse time-course gene expression data

### 2020-06-17 scripts/manuscript.Rmd
More small changes

Once the gene ID to GO mapping list is created, `moanin` provides an 
interface to `topGO` to determine enriched GO terms. **EAP: What does the package do that is an enhancement to topGO output? Would be good to briefly describe** Here, we show an example of
running a GO term enrichment on the "Biological process" ontology (BP).

>>>>

Once the gene ID to GO mapping list is created, `moanin` provides an interface
to `topGO` to determine enriched GO terms. In particular, it performs a
p-value correction and only returns the significant GO-term enrichment in an
easy to use `data.frame` object. Here, we show an example of running a GO term
enrichment on the "Biological process" ontology (BP).
